### 2016-02-19 paper.tex
Title case

{\Large \textbf\newline{Experimental study of a low solidity cross-flow turbine
        at transitional Reynolds numbers: Power production, strut losses, and near-wake
        dynamics}} \newline % Insert author names, affiliations
% and corresponding author email (do not
% include
% titles, positions, or degrees).
\\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1,*}, Budi
Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
NH, 03857, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories, P.O.
Box 5800, Albuquerque, New Mexico 87185-MS1124, USA \\ \bigskip

>>>>

{\Large \textbf\newline{Experimental Study of a Low Solidity Cross-Flow Turbine
        at Transitional Reynolds Numbers: Power Production, Strut Losses, and Near-Wake
        Dynamics}} \newline % Insert author names, affiliations
% and corresponding author email (do not
% include
% titles, positions, or degrees).
\\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1,*}, Budi
Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
NH, 03857, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories,
P.O. Box 5800, Albuquerque, New Mexico 87185-MS1124, USA \\ \bigskip
